\chapter{Evaluation of the functional modules and the product in its entirety, including the failure analysis}
To evaluate the functional modules and the product in its entirety, the feedback given by the client about the program is used. The program is made for the client which means that their feedback is most valuable in evaluating the program. The evaluation of the developers is also used for evaluating the program, because the developers know in which areas the program can improve. 

\section{Program evaluation}
Overall the application that is built is good. It meets the wishes of the client and has an extensive list of features. There are issues in the application which have not been solved. These are discussed below.
\subsection{Vertical spacing}
The fact that the client didn’t want vertical scrolling (i.e. all nodes in the vertical spacing are shown on the screen), caused nodes to be barely visible in locations with many branches. One way to solve this would be to add the ability to also zoom vertically, but this was something which was not desirable for the client at this time. Another option would be to use the vertical space more efficiently and to make the nodes smaller.

\subsection{Usability of the program for biologists}
In terms of speed the program has an outstanding performance, which makes it usable. However, the program has a lot of features, which can be overwhelming for a user.The program needs guidelines for a user to be able to use it. 
Another issue with usability relates to the problem of vertical spacing. Because of this problem, more complicated structures in the graph can be not be explored. 
A big issue for the biologists was finding convergent evolution, and our program can still improve in this area. There is some visual help in finding convergent evolution with the phylogenetic bubbles, but it’s open to improvement.  Highlighting convergent evolution in the graph would be a huge improvement. 

